The Gender Pay Gap in the General Social Survey

### 2023-08-23 Paper/paper.Rmd
CV of 3

``` r
formula <- as.formula(paste("realrinc ~", paste(x_cols_dummys, collapse = " + ")))
mod_full <- train(formula,
                  data = train, 
                  method = "lm",  
                  trControl = trainControl(method = "cv"))
```

@@

``` r
formula2 <- as.formula(paste("log_realrinc ~", paste(x_cols_dummys, collapse = " + ")))
mod_loginc <- train(formula2,
                    data = train, 
                    method = "lm",  
                    trControl = trainControl(method = "cv"))
```

@@

``` r
ridge <- train(formula, data = train,
  method = "glmnet", trControl = trainControl(method = "cv"),
  tuneGrid = expand.grid(alpha = 0, lambda = seq(0, 500, 1))) 
```

@@

To perform the lasso regression in `R` we set $\alpha$ equal to one. The lasso regression yields a lower RMSE than the ridge regression (25,504.58 vs. 25,524.85) and even a lower RMSE than the linear regression.

In a final step we use elastic net regularization which is a linear combination of ridge and lasso regression. The elastic net regularization allows $\alpha$ to vary between zero and one. This results in an RMSE of 25,241.7.

>>>>

``` r
formula <- as.formula(paste("realrinc ~", 
                            paste(x_cols_dummys, collapse = " + ")))
mod_full <- train(formula,
                  data = train, 
                  method = "lm",  
                  trControl = trainControl(method = "cv", number = 3))
```

@@

``` r
formula2 <- as.formula(paste("log_realrinc ~", 
                              paste(x_cols_dummys, collapse = " + ")))
mod_loginc <- train(formula2,
                    data = train, 
                    method = "lm",  
                    trControl = trainControl(method = "cv", number = 3)
```

@@

``` r
ridge <- train(formula, data = train,
  method = "glmnet", trControl = trainControl(method = "cv", number = 3,
  tuneGrid = expand.grid(alpha = 0, lambda = seq(0, 500, 1))) 
```

@@

To perform the lasso regression in `R` we set $\alpha$ equal to one. The lasso regression yields a lower RMSE than the ridge regression (25,504.89 vs. 25,524.85) and even a lower RMSE than the linear regression.

In a final step we use elastic net regularization which is a linear combination of ridge and lasso regression. The elastic net regularization allows $\alpha$ to vary between zero and one. This results in an RMSE of 25,504.18.
